Exposure Consequences - Statistics and Figures

### 2018-07-17 ManuscriptMaterials.Rmd
add counts of interpolated localization data for every angle, to see if we want to remove the 15 degree location

>>>>

## Missing data

Here are the counts of participants with valid localization estimates in all 4 tasks for every hand angle. Missing data occurs here, because we don't extrapolate beyond the range of the data.

```{r localization_count_table}
kable(getLocCountTable())
```

Since the majority of missing data appears to be at the 15 degree location, we exclude that angle from analysis, with a switch in analysis functions `remove15=TRUE`, which can be set to false if we'd want.
